%!TEX root = ../report.tex

\begin{document}
    \begin{abstract}
        Rescue services put their lives at risk trying to save other lives. 
        Therefore, robots and other new technologies are being used to help them do their meaningful work. 
        Point clouds can be employed to monitor the current status of a danger area, and CityGML models to depict its ideal status, 
        supporting rescue services in elaborating an incident action plan. The point cloud and the CityGML model registration is, therefore, of great importance. 

        The existing methods to register a point cloud with a CityGML model do not leverage the CityGML model’s information 
        or only works when the point cloud and the CityGML model are already coarsely registered.

        In this work, the 3D registration problem was converted into a 2D registration problem 
        by projecting the point cloud and the CityGML model's terrain intersection into the xy-plane. 
        In the resulting projection, the lines represented the walls of the 3D space, 
        and the intersections of the lines and their angle were utilized as features to perform the registration. 
        A Mixed Integer Linear Program was then utilized to compute the correspondences between the features and a transformation that aligns them. 
        The obtained transformation was finally extended to be applied in the 3D space.
        The proposed method successfully performs a coarse registration of a point cloud with a CityGML model. 
        Moreover, it can be extended to work with other features to increase its accuracy.

    \end{abstract}
\end{document}
